\documentclass[11pt]{article}

\usepackage[margin=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{multicol}

\newcommand\prn[1]{\left( #1 \right)}
\newcommand\bkt[1]{\left[ #1 \right]}
\newcommand\set[1]{\left\{ #1 \right\}}
\newcommand\abs[1]{\left| #1 \right|}

\pagestyle{empty}

\frenchspacing

\begin{document}

\begin{table}[h]
    \sc
    \large
    \centering 
    \begin{tabular}{rl}
        Math 150:&Calculus with Analytic Geometry I\\
        Semester:&Fall 2017\\
        Instructor:&Christopher Natoli
    \end{tabular}
\end{table}

\section{Details}

\begin{table}[h]
    \begin{tabular}{@{}ll}
        Classroom:&507 Hunter West\\
        Class time:&Monday and Wednesday, 3:10--5:00\textsc{pm}\\
        Office hours:&Wednesday, 2:10--3:10\textsc{pm} in 924 Hunter East\\
        Textbook:&\textit{Essential Calculus} by James Stewart, second edition, with WebAssign\\
        Email:&chrisnatoli@gmail.com (\textit{do not email me at any other address})\\
        Website:&https://chrisnatoli.github.io
    \end{tabular}
\end{table}

\vspace{-0.5cm}

\section{Tentative lecture schedule}

\begin{multicols}{2}
\begin{enumerate} \itemsep -3pt
    \item \S1.3 The Limit of a Function
    \item \S1.4 Calculating Limits
    \item \S1.5 Continuity
    \item \S1.6 Limits involving Infinity
    \item \S2.1 Derivatives and Rates of Change
    \item \S2.2 The Derivative as a Function
    \item \S2.3 Basic Differentiation Formulas
    \item \S2.4 The Product and Quotient Rules
    \item \S2.5 The Chain Rule
    \item \S2.6 Implicit Differentiation
    \item \S2.7 Related Rates
    \item Exam I
    \item \S2.8 Linear Approximations and Differentials
    \item \S3.1 Maximum and Minimum Values
    \item \S3.2 The Mean Value Theorem and
    \item \S3.3 Derivatives and the Shapes of Graphs
    \item \S3.4 Curve Sketching
    \item \S3.5 Optimization Problems
    \item \S3.7 Antiderivatives
    \item Exam II
    \item \S4.1 Areas and Distances
    \item \S4.2 The Definite Integral
    \item \S4.3 Evaluating Definite Integrals
    \item \S4.4 The Fundamental Theorem of Calculus
    \item \S4.5 The Substitution Rule
    \item \S7.1 Areas Between Curves
    \item \S7.2 Volumes
    \item \S7.3 Volumes by Cylindrical Shells
    \item Exam III
\end{enumerate}
\end{multicols}

\section{Homework policy}

Problem sets will be assigned weekly on Wednesdays and due the following Wednesday at 11:59\textsc{pm}. 
All problem sets will be conducted through an online service called WebAssign, which you purchase with the textbook.
The key for this class is ``hunter 3042 6934''.
Late homework will not be accepted, but the lowest problem set score will be dropped from your grade.

\section{Exams}

There will be three exams and one final exam.
The first three exams will cover the material since the last exam,
but the final exam will be cumulative.
Calculators and phones are not allowed on any exams.
The dates of each exam are yet to be decided.
The final exam will be department-wide.

\section{Grading}

10\% problem sets, 90\% exams.
The final exam will be worth two of the other exams.
Your lowest exam grade will be dropped; if the final is the lowest grade, it will be counted as one exam.
If you miss an exam, that will count as your lowest grade, so it will be dropped.



\end{document}
